Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Iter on the paper

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
%\usepackage{hyperref}
\usepackage{minted}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

@@

\paragraph{Project vision}
%
Bridging the gap between machine learning research and applications

@@

\paragraph{The python data ecosystem}
%
In a data analysis pipeline, machine learning is only a tiny bit of the
pipeline, although it is critical.

@@

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{minted}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

@@

\paragraph{Project vision}
%
Scikit-learn was born from the observation that most standard
machine-learning algorithms were out of reach of the users that could
most benefit from them, such as researchers --biologists, climate
scientists, experimental physicists--, developers in the industry --web
services, domain-specific applications-- or any analyst without a strong
training in statistics.
%
Implementations mostly consisted of scattered piece of code to download
on researchers' web pages, with the notable exception a few
statistic-specific environment such as the R language \cite{Rmanual}, or
the Weka java library \cite{hall2009weka}.

Bridging the gap between machine learning research and applications

@@

\paragraph{The Python data ecosystem}
%
In a data analysis pipeline, machine learning is only a tiny bit of the
pipeline, although it is critical.

@@

\begin{figure*}
    \includegraphics[width=.355\linewidth]{wage_data}%
    \hspace*{-.025\linewidth}%
    \hfill%
    \includegraphics[width=.355\linewidth]{wage_data_random_forest}%
    \hspace*{-.025\linewidth}%
    \hfill%
    \includegraphics[width=.355\linewidth]{wage_data_linear_svm}%

\end{figure*}
